Supplementary Materials

### 2023-07-24 manuscript/supplementary.tex
ms updates from italy

\subsection{Locally-Rescaled Fit Results}

@@

\subsection{Strong Selection Grids}
\label{supp:strong-sel-grid}

>>>>

\clearpage
\subsection{Locally-Rescaled Fit Results}

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[]{figures/supplementary/b-rescaling-effect.pdf}

  \caption{Genome-wide average $B(x)$ values across selection coefficients for
  $\mu = 1.58 \times 10^{-8}$, for both the standard (blue) and
locally-rescaled B' (orange) maps. This indicates that locally-rescaling the B'
maps only in practice changes how deep the ``U" is.}

    \label{suppfig:rescale-effects}
\end{figure}

\clearpage
\subsubsection{Locally-Rescaled Model Fit Results}
\label{supp:locally-rescaled-fits}

Below are the model fit results for locally-rescaled model runs, with the
upper mutation rate boundary set to $\mu = 8 \times 10^{-8}$.

\subsubsection*{CHB}

\begin{minipage}{\linewidth}\begin{footnotesize}
\begin{verbatim}
SimplexModel (interpolated w): 6 x 7 x 3
    w grid: [1.000e-11 6.310e-11 3.981e-10 2.512e-09 1.585e-08 1.000e-07] (before interpolation)
    t grid: [1.e-08 1.e-07 1.e-06 1.e-05 1.e-04 1.e-03 1.e-02]
    window size: 1.0 Mbp

  ML estimates: (whole genome)
  standard error method: None
  negative log-likelihood: 61820142829.01206
  number of successful starts: 10000 (100.0% total)
  pi_0 = 0.00106289
  pi  = 0.000752601
  mut. rate  = 8e-08 
  Ne = 26,572 (if μ=1e-8), Ne = 13,286 (if μ=2e-8)
  R² = 60.8648% (in-sample)  59.1654% (out-sample)
  W = 
            CDS    gene    phastcons
  ------  -----  ------  -----------
  1e-08       1   0.991        0
  1e-07       0   0            0
  1e-06       0   0            0
  1e-05       0   0            0.767
  0.0001      0   0            0.03
  0.001       0   0            0.069
  0.01        0   0.008        0.134
\end{verbatim}
\end{footnotesize}\end{minipage}

\subsubsection*{CEU}

\begin{minipage}{\linewidth}\begin{footnotesize}
\begin{verbatim}
SimplexModel (interpolated w): 6 x 7 x 3
    w grid: [1.000e-11 6.310e-11 3.981e-10 2.512e-09 1.585e-08 1.000e-07] (before interpolation)
    t grid: [1.e-08 1.e-07 1.e-06 1.e-05 1.e-04 1.e-03 1.e-02]
    window size: 1.0 Mbp

  ML estimates: (whole genome)
  standard error method: None
  negative log-likelihood: 250647896892.40094
  number of successful starts: 10000 (100.0% total)
  pi_0 = 0.001479
  pi  = 0.00106447
  mut. rate  = 8e-08 
  Ne = 36,974 (if μ=1e-8), Ne = 18,487 (if μ=2e-8)
  R² = 68.7046% (in-sample)  67.8854% (out-sample)
  W = 
            CDS    gene    phastcons
  ------  -----  ------  -----------
  1e-08       1   0.994        0
  1e-07       0   0            0
  1e-06       0   0            0
  1e-05       0   0            0.751
  0.0001      0   0            0.039
  0.001       0   0            0.028
  0.01        0   0.006        0.183
\end{verbatim}
\end{footnotesize}\end{minipage}

\subsubsection*{YRI}

\begin{minipage}{\linewidth}\begin{footnotesize}
\begin{verbatim}
SimplexModel (interpolated w): 6 x 7 x 3
    w grid: [1.000e-11 6.310e-11 3.981e-10 2.512e-09 1.585e-08 1.000e-07] (before interpolation)
    t grid: [1.e-08 1.e-07 1.e-06 1.e-05 1.e-04 1.e-03 1.e-02]
    window size: 1.0 Mbp

  ML estimates: (whole genome)
  standard error method: None
  negative log-likelihood: 197824525643.2897
  number of successful starts: 10000 (100.0% total)
  pi_0 = 0.00111021
  pi  = 0.000801495
  mut. rate  = 8e-08 
  Ne = 27,755 (if μ=1e-8), Ne = 13,877 (if μ=2e-8)
  R² = 62.5591% (in-sample)  61.367% (out-sample)
  W = 
            CDS    gene    phastcons
  ------  -----  ------  -----------
  1e-08       1   0.989        0
  1e-07       0   0.003        0
  1e-06       0   0            0
  1e-05       0   0            0.774
  0.0001      0   0            0.025
  0.001       0   0            0.067
  0.01        0   0.008        0.134
\end{verbatim}
\end{footnotesize}\end{minipage}

\clearpage
\subsection{Strong Selection Grids}
\label{supp:strong-sel-grid}
